Formalizing the Kolmogorov extension Theorem in Lean

### 2024-07-22 Manuscript/proof_outline.tex
better name

\begin{minted}[highlightlines={1-4}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theoremIsSetField_cylinders :IsSetField (cylinders α) 
theorem setRing_cylinders :  IsSetRing (cylinders α)
theorem IsSetSemiringCylinders
  : IsSetSemiring (cylinders α)   
\end{minted}

>>>>

\begin{minted}[highlightlines={1-4}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theoremIsSetField_cylinders :IsSetField (cylinders α) 
theorem isSetRing_cylinders :  IsSetRing (cylinders α)
theorem IsSetSemiringCylinders
  : IsSetSemiring (cylinders α)   
\end{minted}
